Species motif participation provides unique information about species risk of extinction

### 2023-04-04 manuscript/supplement_motifs.tex

\section{Persistence and motif profiles}

@@

    % Updated to use mean instead of all species
    \begin{table}[hb!]
        \caption{Coefficients ($\beta$) for models relating persistence to the proportion of a network profile made up by a focal motif, the level of disturbance to basal resources (corresponding to a probability of extinction ranging between 0.1 and 0.5), and their interaction. Predictors were centered and scaled before model fitting; coefficients refer to a unit increase in predictors. We also provide the marginal $R^2$ value for each regression. }
        \label{motif_profile_tab}
        \centering
        \footnotesize
        \begin{tabular}{c|c c | c c | c c | c c | c }
        & \multicolumn{2}{c|}{Intercept} & \multicolumn{2}{c|}{Proportion} & \multicolumn{2}{c|}{Disturbance} & \multicolumn{2}{c|}{Interaction} & \\
        Motif & $\beta$ & $p$ & $\beta$ & $p$ & $\beta$ & $p$ & $\beta$ & $p$ & $R^2_M$ \\
            \hline
            Omnivory & 0.574 & \textless0.001 & 5.81$\times10^{-3}$ & \textless0.001 & -0.0189 & \textless0.001 & -1.775$\times10^{-7}$ & 0.885 & 0.960 \\
            Apparent competition & 0.574 & \textless0.001 & 7.22$\times10^{-4}$ & \textless0.001 & -0.0189 & \textless0.001 & 5.20$\times10^{-6}$ & 0.003 & 0.964 \\
            Direct competition & 0.574 & \textless0.001 &  1.38$\times10^{-4}$ & \textless0.001 & -0.0189 & \textless0.001 & 1.01$\times10^{-6}$ & 0.400 & 0.964 \\
            Three-species chain & 0.574 & \textless0.001 & 7.22$\times10^{-4}$ & \textless0.001 & -0.0189 & \textless0.001 & 5.20$\times10^{-6}$ & 0.003 & 0.964 \\ 
        \end{tabular}
    \end{table}
\clearpage

@@

     \begin{table}[hb!]
        \centering
        \caption{Coefficients for general linear regressions relating the proportion of each motif in the total motif profile of a network to network size, connectance, and their interaction. Coefficients in \textbf{bold} are significant (\textless0.05). The regression was fit using a binomial error distribution and logit link function.}
       \label{network_prop_lms}
       \begin{tabular}{c|c c c c c}
            Motif & Intercept & Size & Connectance & Interaction \\
            \hline
            Three-species Chain & \textbf{-1.04} & 0.001 & -0.795 & -0.019 \\
            Apparent Competition & 0.168 & -0.002 & -4.09 & 0.010 \\
            Direct Competition & \textbf{-1.42} & -3.69$\times10^{-4}$ & -3.97 & 0.042 \\
            Omnivory & \textbf{-2.99} & 0.003 & \textbf{12.9} & -0.036\\
            \hline
            \end{tabular}
    \end{table}        
\clearpage

>>>>

\section{Persistence and motif profiles} [[updated]]

@@

    % Updated to use mean instead of all species
    \begin{table}[hb!]
        \caption{Coefficients ($\beta$) for models relating persistence to the proportion of a network profile made up by a focal motif, the level of disturbance to basal resources (corresponding to a probability of extinction ranging between 0.1 and 0.5), and their interaction. Coefficients in \textbf{bold} are significant ($\alpha$\textless0.005). Predictors were centered and scaled before model fitting; coefficients refer to a unit increase in predictors. We also provide McFadden's pseudo-$R^2$ value for each regression. }
        \label{motif_profile_tab}
        \centering
        \footnotesize
        \begin{tabular}{c|c c c c c | c }
        Motif & Intercept & Proportion & Disturbance & Interaction &  pseudo-$R^2$ \\
            \hline
            Three-species chain & \textbf{0.326} &  0.0260 & \textbf{-0.595} & -2.53$\times10^{-3}$ & 0.*958 \\
            Apparent competition & \textbf{0.326} & \textbf{0.0501} & \textbf{-0.596} & -2.00$\times10^{-3}$ & 0.962 \\
            Direct competition & \textbf{0.326} & 0.0151 & \textbf{-0.595} & -5.34$\times10^{-4}$ & 0.956 \\
            Omnivory & \textbf{0.326} & \textbf{-0.0626} & \textbf{-0.596} & 3.22$\times10^{-3}$ & 0.966 \\
        \end{tabular}
    \end{table}
\clearpage

@@

     \begin{table}[hb!]
        \centering
        \caption{Coefficients for general linear regressions relating the proportion of each motif in the total motif profile of a network to network size, connectance, and their interaction. Coefficients in \textbf{bold} are significant ($\alpha$\textless0.05). The regression was fit using a binomial error distribution and logit link function.}
       \label{network_prop_lms}
       \begin{tabular}{c|c c c c c}
            Motif & Intercept & Size & Connectance & Interaction \\
            \hline
            Three-species Chain & \textbf{-1.04} & 0.001 & -0.795 & -0.019 \\
            Apparent Competition & 0.168 & -0.002 & -4.09 & 0.010 \\
            Direct Competition & \textbf{-1.42} & -3.69$\times10^{-4}$ & -3.97 & 0.042 \\
            Omnivory & \textbf{-2.99} & 0.003 & \textbf{12.9} & -0.036\\
            \hline
            \end{tabular}
    \end{table}        
\clearpage
